Generality in food webs scales with species richness but not with latitude

### 2015-06-24 manuscript/latitudepaper.tex
found one ref

  The lack of a latitudinal gradient in species richness in this dataset
  contrasts strongly with other
  studies~\citep{Schemske2009,Macpherson2002,Kaufman1995}. As numbers of
  species and links included in a food web vary strongly with sampling effort
  as well as with the underlying diversity of the study area, it is possible
  that the lack of latitudinal trends here is a result of researchers tending
  to expend similar amounts of sampling effort across studies. This could
  result in food webs describing species-rich tropical communities omitting
  more species and links than species-poor arctic communities. In addition, it
  is worth noting that gradients in species richness are generally measured
  for a single taxonomic group at a time
  (e.g.~\citep{Schemske2009,Macpherson2002,Kaufman1995}). It is possible that
  these taxa are not well-represented in our food webs and that the dominant
  taxa in them do not have an underlying latitudinal gradient in richness.  In
  either case, the lack of a strong association between species richness and
  latitude in any ecosystem type means that any effect of latitude on other
  scaling  relationships is not being driven by an underlying  latitudinal
  gradient in species richness. The lack of confounding effects of latitude
  allows us to  more clearly assess effects of latitude on scaling with
  species richness and proportions of species in different  trophic levels.

@@

  The scaling of link density, generality and vulnerability with proportions
  of species at different trophic levels, however, did not differ between lakes
  and most other food webs. Indeed, there was comparatively little variation in
  scaling with the trophic-level breakdown of a web across ecosystem types.
  Terrestrial food webs tended to exhibit less change in scaling over latitude
  than other ecosystem types, as did marine webs when considering scaling with
  the proportion of basal resources. More excitingly, the negative relationships
  between the proportion of top predators in a web and link density and
  vulnerability were weaker (i.e., the scaling exponent was more strongly
  negative) in low-latitude stream ecosystems. This may imply that top predators
  in high-latitude streams tend to be more generalist than their low-latitude equivalents.
  More generally, the lack of correspondence between the scaling of food-web
  properties with species richness and with proportions of species at each
  trophic level suggests that the size and trophic breakdowns of a community can
  provide different information about the breadth of niches in that community.

>>>>

  The lack of a latitudinal gradient in species richness in this dataset
  contrasts strongly with other
  studies~\citep{Schemske2009,Macpherson2002,Kaufman1995}. As numbers of
  species and links included in a food web vary strongly with sampling effort
  as well as with the underlying diversity of the study area, it is possible
  that the lack of latitudinal trends here is a result of researchers tending
  to expend similar amounts of sampling effort across studies. This could
  result in food webs describing species-rich tropical communities omitting
  more species and links than species-poor arctic communities. In addition, it
  is worth noting that gradients in species richness are generally measured
  for a single taxonomic group at a
  time~\citep[e.g.]{Schemske2009,Macpherson2002,Kaufman1995}. It is possible
  that these taxa are not well-represented in our food webs and that the
  dominant taxa in them do not have an underlying latitudinal gradient in
  richness.In either case, the lack of a strong association between species
  richness and latitude in any ecosystem type means that any effect of
  latitude on other scalingrelationships is not being driven by an
  underlyinglatitudinal gradient in species richness. The lack of confounding
  effects of latitude allows us tomore clearly assess effects of latitude on
  scaling with species richness and proportions of species in differenttrophic
  levels.

@@

  The scaling of link density, generality and vulnerability with proportions
  of species at different trophic levels, however, did not differ between lakes
  and most other food webs. Indeed, there was comparatively little variation in
  scaling with the trophic-level breakdown of a web across ecosystem types.
  Terrestrial food webs tended to exhibit less change in scaling over latitude
  than other ecosystem types, as did marine webs when considering scaling with
  the proportion of basal resources. More excitingly, the negative relationships
  between the proportion of top predators in a web and link density and
  vulnerability were weaker (i.e., the scaling exponent was more strongly
  negative) in low-latitude stream ecosystems. This may imply that top predators
  in high-latitude streams tend to be more generalist than their low-latitude
  equivalents~\citep{Winemiller2008}.
  More generally, the lack of correspondence between the scaling of food-web
  properties with species richness and with proportions of species at each
  trophic level suggests that the size and trophic breakdowns of a community can
  provide different information about the breadth of niches in that community.
